\begin{problem}{}{}{Real Mathematical Analysis, Pugh, Ex.85 p.133}
Suppose that \(M\) is compact and that \(\mathcal{U}\) is an open covering of \(M\) which is
``redundant'' in the sense that each \(p \in M\) is contained in at least two members
of \(\mathcal{U}\). Show that \(\mathcal{U}\) reduces to a finite subcovering with the same property.
\end{problem}

\begin{solution}
Since $M$ is compact and $\mathcal{U}$ is an open covering of $M$, $\mathcal{U}$ reduces to some $V$, 
where $V$ is a finite subcovering.
Suppose there are points in $M$ that belong to exactly one member of $V$. Let's call this set of points $A$.

The idea is to add extra patches from $\mathcal{U}$ that are not in $V$ to cover the points in $A$. 
For each $p \in A$, it is possible to add a set $U \in \mathcal{U}$ with $U \notin V$, such that $p \in U$, 
since $\mathcal{U}$ is redundant. Adding such a set for each $p \in A$ would ensure each point of $M$ is covered by at least two sets.

If $A$ is finite, then we only need to add a finite number of extra patches to $V$, 
and $V$ would become a redundant finite subcovering of $M$.

However, it is possible that $A$ is infinite, meaning we might need to add infinitely many extra sets to $V$, 
which makes $V$ no longer a finite subcovering. Let's show that even if $A$ is infinite, we only need to add 
a finite number of extra patches to $V$.

We claim that $A$ is compact. Consider a sequence $(p_n)$ in $A$. Since $M$ is compact, 
$(p_n)$ has a convergent subsequence $(p_{n_k})$, such that $(p_{n_k}) \to p$, where $p \in M$. Suppose $p \notin A$. 
This means $p$ belongs to at least two members from $V$. Let $V_1, V_2$ be two sets that contain $p$. 
We have that $V_1 \cap V_2$ is open since a finite intersection of open sets is open. 
There exists $r > 0$ such that the neighborhood $M_{r}p  \subset V_1 \cap V_2$. Since $(p_{n_k}) \to p$, 
there must be terms of $(p_{n_k})$ that lie in $M_{r}p$, which in turn lie in $V_1 \cap V_2$. 
This contradicts the fact that $(p_{n_k})$ is in $A$ (because points in $A$ belong to exactly one set). 

Therefore, $p \in A$ and $A$ is compact. Now, since $A$ is compact, 
the collection of extra patches we selected to cover $A$ is an open cover of $A$, 
and it must reduce to a finite subcovering for $A$. 

By this construction, our original finite cover $V$ plus this finite subcovering for $A$ ensures 
that $\mathcal{U}$ reduces to a redundant finite subcovering.
\end{solution}